### 2022-10-15 chapters/conclusion.tex
add : some drafts for perspectives

\begin{enumerate}
      \item  vulgarisation of the energy consumption -> abstract numbers aren't enough
      \item Deeper analysis for some web frameworks ( what is the reason behind an increase in power consumption while scaling )

>>>>

\paragraph{raising awareness of the energy consumption of the Softwares}
While this thesis's main focus was to optimize energy consumption using comparative studies, it was easier to say that approach X is greener than approach Y no matter which metric we were using. however, it won't be the case for developers while measuring the energy consumption of their programs, some tried to give labels such as (A,B,C ..etc) while others transtaled this raw metrics in an equivalent of a fuel consumption (e.g. 1 liter of fuel per 1000 lines of code). most of the approaches where to use the carbon emmision, such as\cite{patterson2021carbon} or ecograder~\link{https://ecograder.com/}
we will explore these approaches and see how they can be used to rise the awareness of the energy consumption of their code

\begin{enumerate}

      \item Deeper analysis for some web frameworks ( what is the reason behind an increase in power consumption while scaling )
